My title

### 2024-10-17 paper/paper.qmd
Year 2018|2022 - analysis complete.

library(boot)
library(broom.mixed)
library(collapse)
library(dataverse)
library(gutenbergr)
library(janitor)
library(knitr)
library(marginaleffects)
library(modelsummary)
library(rstanarm)
library(tidybayes)
library(tidyverse)
df <- read.csv(here::here("data/02-analysis_data/analysis_data.csv"))

```

```{r}
#| warning: false
#| message: false
labeled_df |>
  ggplot(aes(x = label_education, fill = label_outcome)) +
  stat_count(position = "dodge") +
  facet_wrap(facets = vars(label_sex)) +
  theme_minimal() +
  labs(
    x = "Highest education",
    y = "Number of respondents",
    fill = "Mental Depression"
  ) +
  coord_flip() +
  scale_fill_brewer(palette = "Set2") +
  theme(legend.position = "bottom")
```
```{r}
#| warning: false
#| message: false
mental_illness <- readRDS(file = here::here("models/mental_illness.rds"))

# Introduction

@@

## Overview

@@

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

@@

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

@@

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

@@

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

>>>>

library(boot)
library(broom.mixed)
library(collapse)
library(dataverse)
library(gutenbergr)
library(janitor)
library(knitr)
library(marginaleffects)
library(modelsummary)
library(rstanarm)
library(tidybayes)
library(tidyverse)
# df <- read.csv(here::here("data/02-analysis_data/analysis_data.csv"))
labeled_df <- read.csv(here::here("data/02-analysis_data/model_data_sample_2k.csv"))
```
# Introduction

@@

```{r}
#| label: fig-education
#| fig-cap: Education
#| warning: false
#| message: false
#| echo: false
labeled_df |>
  ggplot(aes(x = label_education, fill = label_outcome)) +
  stat_count(position = "dodge") +
  facet_wrap(facets = vars(label_sex)) +
  theme_minimal() +
  labs(
    x = "Highest education",
    y = "Number of respondents",
    fill = "Mental Depression"
  ) +
  coord_flip() +
  scale_fill_brewer(palette = "Set2") +
  theme(legend.position = "bottom")
```
## Overview

@@

# ggplot(penguins, aes(x = island, fill = species)) +
#   geom_bar(alpha = 0.8) +
#   scale_fill_manual(values = c("darkorange","purple","cyan4"),
#                     guide = "none") +
#   theme_minimal() +
#   facet_wrap(~species, ncol = 1) +
#   coord_flip()
```

@@

# analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
# 
# analysis_data |> 
#   ggplot(aes(x = width, y = length)) +
#   geom_point(alpha = 0.8) +
#   theme_minimal() +
#   labs(x = "Wing width (mm)",
#        y = "Wing length (mm)")
```

@@

Our results are summarized in @tbl-lrmodelresults.

```{r}
#| warning: false
#| message: false
#| echo: false
#| eval: true
#| label: tbl-lrmodelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
mental_illness <- readRDS(file = here::here("models/mental_illness.rds"))

@@

# modelsummary::modelsummary(
#   list(
#     "First model" = first_model
#   ),
#   statistic = "mad",
#   fmt = 2
# )
```

@@

# pp_check(first_model) +
#   theme_classic() +
#   theme(legend.position = "bottom")
# 
# posterior_vs_prior(first_model) +
#   theme_minimal() +
#   scale_color_brewer(palette = "Set1") +
#   theme(legend.position = "bottom") +
#   coord_flip()
```

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2
# 
# plot(first_model, "trace")
# 
# plot(first_model, "rhat")
```
